---
title: "Vega in RMarkdown"
output: html_document
---

This page is generated from an `Rmarkdown` file using an example from the [Vega gallery](https://vega.github.io/vega/examples/brushing-scatter-plots/). 

The plotting works out of the box with `r2d3`. As far as I know, any Vega plot can directly be used with no difficulty.

```{r setup, include=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproduce the Example Plot

Read in some nice `JSON` data. This will be passed to `r2d3::r2d3`, then can magically be directly referred to in the script that specifies the Vega visualisation, `iris-interaction.js`.

```{r}
data = jsonlite::toJSON(jsonlite::read_json("data/iris.json"))
```

The below chunk would usually produce a normal `r2d3` plot, but the `height` of the `container` element `r2d3` exposes is set to `0`. This is fine as `iris-interaction.js` does not refer to the container element `r2d3` exposes.

```{r}
# Include vega as a dependency
# Set the height as 0 so the html element produced has no height 
# The visualisation hooks into a div defined below as it must have a static id
r2d3::r2d3(data = data, script = "iris-interaction.js", dependencies = "lib/vega.min.js", height = 0)
```

Here I attach a global `div` directly to the markdown page. You can't see it, but it's literally right below this line, which is why the visualisation has hooked into it. Look at the raw `Rmd` to confirm.

<div id='iris-container'></div>

The `div` is given an `id` which is specified in `iris-interaction.js`, again just as in the standard Vega example. The `js` file looks exactly like this

```
var spec = { ... };

var view = new vega.View(vega.parse(spec), {
  loader: vega.loader({baseURL: '/vega/'}),
  logLevel: vega.Warn,
  renderer: 'canvas'
})
// Here I specify the html element to drop the visualisation in
.initialize('#iris-container').hover().run(); 

```

If you know the proper way to do this, please let me know! 

Akhil